---
title: "Functions"
author: "mysteryTurtle"
date: "6/21/2021"
output: pdf_document
---

## Functions Intro
```{r}

# function 1
add2 <- function(x, y) {
        x + y
}

# function 2
above10 <- function(x) {
        use <- x > 10 # logical vector of T/F
        x[use] # subsets the vector w/ use
}

# function 3
above <- function(x, n = 10) {
        use <- x > n
        x[use] # returns all numbers > n
}

# function 4
columnmean <- function(y, removeNA = TRUE) {
        nc <- ncol(y)
        means <- numeric(nc) # empty vector with all zeros
        
        for(i in 1:nc) {
                means[i] <- mean(y[,i], na.rm = removeNA)
        }
        means # returns, since is last exp
}
```

## Functions (More notes)
- defined by function()

```{r}
f <- function() {
        # empty function
}

f <- function(num) {
        for(i in seq_len(num)) {
                cat("Hello, world!\n")
        }
}

# returns total num of characters printed to console
f <- function(num = 1) {
        hello <- "Hello, world!\n"
        for(i in seq_len(num)) {
                cat(hello)
        }
        chars <- nchar(hello) * num
        chars
}
f()
f(2)
meaningoflife <- f(3)
print(meaningoflife)
```

## Argument Matching
- matched positionally || name


## The ... argument
- variable number of arguments passed on to other functions
- used when extending another function and you don't want to copy the entire argument list of the original function
- arguments that appear after ... on the argument list must be named explicitly and cannot be partially matched or matched positionally

```{r}
myplot <- function(x, y, type = '1', ...) {
        plot(x, y, type = type, ...)
}

```





